Baseline centering problem

### 2018-12-21 paper/tangotd.tex

>>>>

The above can be turned to an infinite-rank approximation by writing
\begin{equation}
\transp{1_{s_1}}Z\psi=\E_{s_2\sim \rho}\, \E_{\omega}\,
\green(s_1,\omega)f(s_2,\omega)\psi(s_2)
\end{equation}
where integration is over $\omega$ in an arbitrary space (eg $\omega\in
[0;1]$ or $\omega\in \R^d$ with Gaussian distribution). This amounts to
sending each state to a function over $\omega$, and using the dot product
from $L^2(\omega)$. This should solve some kernel/image issues and
increase representational power. The equation
$\Id=F\Delta\transp{\green}$ becomes $\delta_{\omega\omega'}=\E_{s\sim
\rho, \,s'\sim P(s'|s)}
f(s,\omega)(\green(s,\omega')-\green(s',\omega'))$ TODO CHECK, which is not easy to
solve because of the singular $\delta_{\omega\omega'}$, but should be better with things on the right and left.
